Measurement of the Negative Pion and Positive Kaon Total Hadronic Cross Sections on Argon at the LArIAT Experiment

### 2018-12-30 Chapter-6/6-PionCrossSection.tex
s
half of lariat prel

The top panel of Figure \ref{fig:FinalXSResPion} shows the cross section obtained combining the two datasets. To combine the datasets, we merge the corrected interacting histogram for the 60A data with the corrected interacting histogram for the 100A data; we apply the same merging with the incident histograms. We then calculate the cross section central point and statistical uncertainty using the merged interacting and incident histograms. The systematic uncertainty is calculated as the sum in quadrature of the original systematic uncertainties on the cross section measurements on the two separated data sets. Again, with the exception of the highest energy bins (energy greater than 800 MeV), the systematic uncertainties are the dominant uncertainties; the lion's share of the systematic uncertainty results from our uncertainty on the beam composition, which we plan to constrain with different beamline data in a future iteration of the analysis.

>>>>

The top panel of Figure \ref{fig:FinalXSResPion} shows the cross section obtained combining the two datasets. To combine the datasets, we merge the corrected interacting histogram for the 60A data with the corrected interacting histogram for the 100A data; we apply the same merging with the incident histograms. We then calculate the cross section central point, statistical uncertainty and systematic uncertainty relative to the kinetic energy using the merged interacting and incident histograms. The systematic uncertainty relative to the corrections is calculated as the sum in quadrature of the original systematic uncertainties on the cross section measurements on the two separated data sets. Again, with the exception of the highest energy bins (energy greater than 800 MeV), the systematic uncertainties are the dominant uncertainties; the lion's share of the systematic uncertainty results from our uncertainty on the beam composition, which we plan to constrain with different beamline data in a future iteration of the analysis.

### 2018-12-30 Drafting.tex
s
half of lariat prel

%\linenumbers
\begin{document}
\begin{equation}
E^{\text{kin}}_{\text{Front Face}} = \sqrt{p_{Beam}^2 + m_{Beam}^2} - m_{Beam}^2 - E_{Loss} 
\end{equation}

\begin{document}

@@

\begin{equation}
E_{i} = \sqrt{p_{Beam}^2 + m_{Beam}^2} - m_{Beam}^2 - E_{Loss} - E_{\text{dep FF-i}}
\end{equation}

\begin{equation}
\delta E_{i} = \sqrt{\delta p_{Beam}^2 + \delta E_{Loss}^2 +  \delta  E_{\text{dep FF-i}}^2}
\end{equation}

\begin{equation}
E_{\text{dep FF-i}} = \sum_{j<i} E_{\text{dep i}}  \Rightarrow \delta E_{\text{dep FF-i}} = (i -1) \delta E_{\text{dep i}}
\end{equation}

@@

>>>>

%\linenumbers
\begin{document}

\begin{align}
C^{\text{$\pi$ MC}}_{\text{Int}} (E_{i}) &= \frac{N^{\text{$\pi$ MC}}_{\text{Int}} (E_{i})}{N^{\text{TOT MC}}_{\text{Int}} (E_{i})}\\
&= \frac{ N^{\text{TOT MC}}_{\text{Int}} (E_{i}) - B^{\text{TOT MC}}_{\text{Int}} (E_{i}) }{N^{\text{TOT MC}}_{\text{Int}} (E_{i})}
\end{align}

\begin{align}
C^{\text{$\pi$ MC}}_{\text{Inc}} (E_{i}) &= \frac{N^{\text{$\pi$ MC}}_{\text{Inc}} (E_{i})}{N^{\text{TOT MC}}_{\text{Inc}} (E_{i})}\\
&= \frac{ N^{\text{TOT MC}}_{\text{Inc}} (E_{i}) - B^{\text{TOT MC}}_{\text{Inc}} (E_{i}) }{N^{\text{TOT MC}}_{\text{Inc}} (E_{i})}
\end{align}

\begin{equation}
E^{\text{kin}}_{\text{Front Face}} = \sqrt{p_{Beam}^2 + m_{Beam}^2} - m_{Beam} - E_{Loss} 
\end{equation}

\begin{equation}
U^\text{Int} _{i, j} (E_i) 
\end{equation}

\begin{equation}
U^\text{Inc} _{i, j} (E_i) 
\end{equation}

@@

\begin{equation}
E_{i} = \sqrt{p_{Beam}^2 + m_{Beam}^2} - m_{Beam} - E_{Loss} - E_{\text{dep FF-j}}
\end{equation}

\begin{equation}
E_{\text{slice j}} = \sqrt{p_{Beam}^2 + m_{Beam}^2} - m_{Beam} - E_{Loss} - E_{\text{dep FF-j}}
\end{equation}

\begin{equation}
\delta E_{\text{slice j}} = \sqrt{\delta p_{Beam}^2 + \delta E_{Loss}^2 +  \delta  E_{\text{dep FF-j}}^2}
\end{equation}

\begin{equation}
E_{\text{dep FF-j}} = \sum_{j<s} E_{\text{dep s}}  \Rightarrow \delta E_{\text{dep FF-j}} = (j -1) \delta E_{\text{dep s}}
\end{equation}

@@

\begin{equation}
P_\text{Int} = \frac{N_\text{Int}}{N_\text{Inc}} = 1 - e^{-\sigma_\text{TOT} \text{ n }\delta X} 
\end{equation}

\begin{equation}
\sigma_\text{TOT}(E)  \sim \frac{1}{\text{ n }\delta X} \frac{N_\text{Int}}{N_\text{Inc}}
\end{equation}

\begin{equation}
\sigma_\text{TOT}(E_i)  = \frac{1}{\text{ n }\delta X} \frac{N^{\pi^-}_\text{Int}(E_i)}{N^{\pi^-}_\text{Inc}(E_i)}
\end{equation}

\begin{equation}
\mathcal{L}(\mu_0; \sigma^2_0; \Delta\theta_0, \Delta\theta_1) = \prod^1_{i=0} f_X(\Delta\theta_i, \mu_0, \sigma^2_0 ) \Rightarrow 
\end{equation}

\begin{equation}\log{\mathcal{L}} = -\frac{1}{2}\log(2\pi) - \log{\sigma_0} - \frac{1}{2}\frac{(\Delta\theta_0 - \mu_0)^2}{\sigma^2_0} + \text{same for $\Delta\theta_1$}
\end{equation}

\begin{table}[]
\centering
\begin{tabular}{|l|c|c|}
\hline
                     & Low E Beam          & High E Beam\\ \hline
G4Pions       &   70.9 \%          &       82.3 \%         \\ \hline
G4Muons     &   14.6 \%           &      13.5 \%         \\ \hline
G4Electrons &   14.5 \%           &       4.2 \%         \\ \hline
\end{tabular}
\caption{Simulated beamline composition per magnet settings}
\label{tab:beamline}
\end{table}

\begin{table}[b]
\centering
\begin{tabular}{|l|c|}
\hline
                                                        & Run-II Neg Pol     \\ \hline
1. Events Reconstructed in Beamline        &  158396    \\ \hline
2. Events with Plausible Trajectory            &   147468   \\ \hline
3. Beamline $\pi^-/\mu^-/e^-$  Candidate  &   138481    \\ \hline
4. Events Surviving Pile Up Filter              &   108929        \\ \hline
5. Events with WC2TPC Match                 &    41757   \\ \hline
6. Events Surviving Shower Filter             &    40841       \\ \hline
7. Available Events For Cross Section      &   40841       \\ \hline
\end{tabular}
\caption{Number of data events for Run-II Negative and Positive polarity }
\label{tab:beamlineDataSelection}
\end{table}

### 2018-12-30 thesis_main.tex
s
half of lariat prel

\usepackage{multirow}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{appendix}
\usepackage{comment}
\usepackage{cite}
\usepackage{color}
\bibliographystyle{plain}
\usepackage{slashed}

@@

% Need to define title before the abstract.
\title{Measurement of ($\pi^-$-Ar) and ($K^+$-Ar) total hadronic cross sections at the LArIAT experiment}
\author{Elena Gramellini}
\advisor{Bonnie T. Fleming}
\date{December 2018} % usually not \today.

@@

This thesis presents two measurements performed for the first time: the measurement of ($\pi^-$-Ar) total hadronic cross section in the 100-1050 MeV kinetic energy range and the measurement of the ($K^+$-Ar) total hadronic cross section in the 100-650 MeV kinetic energy range. The analyses devised for these measurements use both the core elements of LArIAT: beamline and LArTPC. The first step in each analysis is the development of an event selection based on  beamline and TPC information geared towards the identification of the hadron of interest. We then proceed to match the beamline candidate to a suitable TPC track. Finally,  we apply the ``thin slice method" technique and measure the cross section, correcting for background contamination and detector effects. The thin slice technique is a new method to measure hadron-argon cross sections possible only due to the combination of the tracking and calorimetry capability of the LArTPC technology. 
Albeit never on argon, the hadronic cross section of pions has been extensively measured before on lighter and heavier different elements in thin target experiments, leading to solid predictions for measurements on argon. Through the use of a different technique, our measurement of the  ($\pi^-$-Ar) total hadronic cross section is in general agreement with the predictions by the Geant4 Bertini Cascade model which are based on data from thin target experiments. On the contrary, cross section measurements for kaons are extremely scarce, thus more difficult to model. Our measurement of the  ($K^+$-Ar) total hadronic cross section is mostly in tension with the Geant4 prediction over the explored range of energies and provides new experimental data to properly compare existing interaction models.

@@

The ($\pi^-$-Ar) and the ($K^+$-Ar) total hadronic cross measurements are the first physics results of the LArIAT experiment and will be the basis for the future LArIAT measurements of pion and kaon cross sections in the exclusive channels.
The outcome of these measurements will ultimately enable to quantify and reduce the systematic associated with the hadronic interaction models in neutrino-argon interactions.

>>>>

\usepackage{multirow}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{appendix}
\usepackage{comment}
\usepackage{cite}
\usepackage{color}
\bibliographystyle{plain}
\usepackage{slashed}  
\usepackage{url}
\usepackage{hyperref}

@@

% Need to define title before the abstract.
\title{Measurement of the Negative Pion and Positive Kaon Total Hadronic Cross Sections on Argon at the LArIAT Experiment}
\author{Elena Gramellini}
\advisor{Bonnie T. Fleming}
\date{December 2018} % usually not \today.

@@

This thesis presents two measurements performed for the first time: the measurement of the negative pion total hadronic cross section on argon in the 100-1050 MeV kinetic energy range and the measurement of the positive kaon total hadronic cross section on argon in the 100-650 MeV kinetic energy range. The analyses devised for these measurements use both the core elements of LArIAT: beamline and LArTPC. The first step in each analysis is the development of an event selection based on  beamline and TPC information geared towards the identification of the hadron of interest. We then proceed to match the beamline candidate to a suitable TPC track. Finally,  we apply the ``thin slice method" technique and measure the cross section, correcting for background contamination and detector effects. The thin slice technique is a new method to measure hadron-argon cross sections possible only due to the combination of the tracking and calorimetry capability of the LArTPC technology. 
Albeit never on argon, the hadronic cross section of pions has been extensively measured before on lighter and heavier different elements in thin target experiments, leading to solid predictions for measurements on argon. Through the use of a different technique, our measurement of the negative pion total hadronic cross section on argon is in general agreement with the predictions by the Geant4 Bertini Cascade model which are based on data from thin target experiments. On the contrary, cross section measurements for kaons are extremely scarce, thus more difficult to model. Our measurement of the  positive kaon total hadronic cross section on argon is mostly in tension with the Geant4 prediction over the explored range of energies and provides new experimental data to properly compare existing interaction models.

@@

The negative pion and the positive kaon total hadronic cross measurements are the first physics results of the LArIAT experiment and will be the basis for the future LArIAT measurements of pion and kaon cross sections in the exclusive channels.
The outcome of these measurements will ultimately enable to quantify and reduce the systematic associated with the hadronic interaction models in neutrino-argon interactions.
